Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-13 proposal/mprop.tex
Complete reserach questions and contributions section

@@

\begin{itemize}
\item Background briefly explain the context of the project problem
\item Problem statement and justification. Clearly state the problem to be addressed in your forthcoming project.
  Explain why it would be worthwhile to solve this problem.

\item Research questions and contributions
\item Structure of the rest of the document
\end{itemize}

>>>>

Even though there have been many studies related to issue/ticket quality,
most of them have looked at it qualitatively, not quantitatively (e.g. 
\citet{bettenburg2008makes}, \citet{bettenburg2007quality}). This is 
the first contribution of our study - we will explore the area of 
ticket quality from a statistical point of view, not through interviews
or other human-centered data gathering (i.e. we want to inspect several
open source repositories and collect tickets through the issue tracking
system's APIs).

Moreover, another contribution that our study is trying to bring is that,
even though most studies so far have looked solely at ticket 
features/components, we want to inspect both tickets and other components
of the software project, such as version control system and how various
attributes affect the time-to-close for a particular ticket.

The third contribution that this research tries to achieve is to
propose a model for bug reports and/or feature requests. After collecting
data and finding which components together with their afferent attributes
make for a high quality ticket, we will propose a model for best practices
in terms of creating tickets.

@@
